---
title: "Dependencies"
author: "CE"
date: "17/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(pander)
library(renv)
library(gtools)
rm(list = ls())
```

Here are the direct dependencies.

```{r direct, echo=FALSE, message=FALSE, cache=FALSE}
### little script to help monitor dependencies

### this gets direct dependencies
renv::dependencies(progress = FALSE,
                   dev = TRUE) %>% 
  as_tibble() -> tmpTibDirectDependencies

tmpTibDirectDependencies %>% 
  group_by(Dev, Package) %>% 
  summarise(n = n()) %>% 
  arrange(Dev, desc(n)) %>%
  mutate(i = row_number()) %>%
  select(i, everything()) -> tmpTibDirectDependencies2

tmpTibDirectDependencies2 %>%
  pander::pander(justify = "rllr")

tmpTibDirectDependencies2 %>%
  select(Package) %>%
  pull() -> tmpVecDirectDependencies
```

```{r all, echo=FALSE, message=FALSE, results="hide", cache=FALSE}
### this gets indirect dependencies as well as direct ones
gtools::getDependencies("CECPfuns",
                       c("Depends", "Imports", "LinkingTo", "Suggests"),
                       base = TRUE,
                       recommended = TRUE) %>%
  as_tibble() %>%
  rename(Package = value) %>%
  arrange(Package) %>%
  mutate(i = row_number()) %>%
  select(i, Package) -> tmpTibAllDependencies

tmpTibAllDependencies %>% 
  pander::pander(justify = "rl")

tmpTibAllDependencies %>% 
  select(Package) %>%
  pull() -> tmpVecAllDependencies
```

And here are the indirect dependencies (only).

```{r indirect, echo=FALSE, message=FALSE, cache=FALSE}
tmpTibAllDependencies %>% 
  select(Package) %>%
  pull() -> tmpVecAllDependencies

setdiff(tmpVecAllDependencies, tmpVecDirectDependencies) %>%
  as_tibble() %>%
  rename(Indirect = value) %>%
  arrange(Indirect) %>%
  mutate(i = row_number()) %>%
  select(i, Indirect) -> tmpTibIndirectDependencies

tmpTibIndirectDependencies %>%
  pander::pander(justify = "rl")
```

So we have `r nrow(tmpTibAllDependencies)` dependencies in all, of which
`r nrow(tmpTibDirectDependencies2)` are direct, and 
`r nrow(tmpTibIndirectDependencies)` are indirect.

For reasons I haven't sussed out yet, there is a discrepancy there!  The ones found by `renv::dependencies()` but not by
`gtools::getDependencies()` are these.

```{r weirdness, echo=FALSE}
setdiff(tmpVecDirectDependencies, tmpVecAllDependencies) %>%
  as_tibble() %>%
  rename(Package = value) %>%
  arrange(Package) %>%
  mutate(i = row_number()) %>%
  select(i, Package) %>%
  pander::pander(justify = "rl")
```
