---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CECPfuns)
```

# Introduction to the CECPfuns package

I need to write stuff here!

# Stuff from https://r-pkgs.org/vignettes.html

### 11.6 Advice for writing vignettes

*If you’re thinking without writing, you only think you’re thinking. — Leslie Lamport*

When writing a vignette, you’re teaching someone how to use your package. You need to put yourself in the readers’ shoes, and adopt a “beginner’s mind”. This can be difficult because it’s hard to forget all of the knowledge that you’ve already internalised. For this reason, I find teaching in-person a really useful way to get feedback on my vignettes. Not only do you get that feedback straight away but it’s also a much easier way to learn what people already know.

A useful side effect of this approach is that it helps you improve your code. It forces you to re-see the initial onboarding process and to appreciate the parts that are hard. Every time that I’ve written text that describes the initial experience, I’ve realised that I’ve missed some important functions. Adding those functions not only helps my users, but it often also helps me! (This is one of the reasons that I like writing books).

I strongly recommend literally anything written by Kathy Sierra. Her old blog, 
[Creating passionate users](https://headrush.typepad.com/) is full of advice about programming, teaching, and how to create valuable tools. I thoroughly recommend reading through all the older content. Her new blog, [Serious Pony](https://seriouspony.com/blog/), doesn’t have as much content, but it has some great articles.

If you’d like to learn how to write better, I highly recommend [Style: Lessons in Clarity and Grace](https://amzn.com/0321898680) by Joseph M. Williams and Joseph Bizup. It helps you understand the structure of writing so that you’ll be better able to recognise and fix bad writing.

Writing a vignette also makes a nice break from coding. In my experience, writing uses a different part of the brain from programming, so if you’re sick of programming, try writing for a bit. (This is related to the idea of [structured procrastination](http://www.structuredprocrastination.com/.).
11.6.1 Organisation

For simpler packages, one vignette is often sufficient. But for more complicated packages you may actually need more than one. In fact, you can have as many vignettes as you like. I tend to think of them like chapters of a book - they should be self-contained, but still link together into a cohesive whole.

Although it’s a slight hack, you can link various vignettes by taking advantage of how files are stored on disk: to link to vignette abc.Rmd, just make a link to abc.html.
